Analysis of pleiotropy of eQTLs

### 2023-01-16 presentation_230120_internal_seminar/intern_sem_230120.tex
internal seminar

% full size table is table
        \begin{table}[!tbp]
            \centering
            \footnotesize
            \csvreader[separator=tab,
            tabular=crclcp{0.4\textwidth},
            head,
            table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Marker & \bfseries GWAS Categories\\\hline,
            ]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
                {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
            \vspace{15pt}
        \end{table}

@@

        \begin{itemize}
            \item Pleiotropic regions involving 6 or more GWAS classes
            \item Regions were built with a sliding window of 1e5 nt
        \end{itemize}

% full size table is table
        \begin{table}[!tbp]
            \centering
            \footnotesize
%\hline
            \csvreader[
                separator=tab,
                tabular=p{0.02\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.05\textwidth}p{0.45\textwidth},
                head,
                table head=\bfseries Chr. & \bfseries Start & \bfseries End & \bfseries Cytob. & \bfseries GWAS Categories\\\hline,
            ]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_window_ms.tsv}{}% use head of csv as column names
            {\csvcoli\ & \csvcolv\ & \csvcolvi\ & \csvcoliv\ & \csvcolvii}% specify your coloumns here
%\hline
%
            \vspace{15pt}
        \end{table}
    \end{frame}

>>>>

% full size table is table
        \begin{table}[!tbp]
            \centering
            \footnotesize
            \csvreader[separator=tab,
            tabular=crclcp{0.4\textwidth},
            head,
            table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Known eQTL gene & \bfseries GWAS Categories\\\hline,
            ]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
                {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
            \vspace{15pt}
        \end{table}

@@

% full size table is table
        \begin{table}[!tbp]
            \centering
            \footnotesize
%\hline
            \csvreader[
                separator=tab,
                tabular=p{0.005\textwidth}p{0.05\textwidth}p{0.05\textwidth}p{0.05\textwidth}p{0.05\textwidth}p{0.5\textwidth},
                head,
                table head=\bfseries Chr. & \bfseries Start & \bfseries End & \bfseries Cytob. & \bfseries Known eQTL gene & \bfseries GWAS Categories\\\hline,
            ]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_window_ms.tsv}{}% use head of csv as column names
            {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
            \vspace{15pt}
            \caption{Pleiotropic regions involving 6 or more GWAS classes. These regions were built with a sliding window of 1e5 nt. Genomic coordinates are given for the hg38 assembly.}\label{tab:pleiotropic_regions}
        \end{table}
